---
title: "Data Product Pitch"
author: "Hao Zhe Liu"
date: "7/1/2020"
output: 
  ioslides_presentation: 
    smaller: yes
    widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
data(mtcars)

modelList <- function(){
  tgt = "mpg"
  featureList = colnames(mtcars)
  featureList = featureList[featureList != tgt]
  lmFormula = paste0(tgt, "~") 
  
  modelList = list(NULL)
  formulaList = list(NULL)
  mseList = list(NULL)
  
  while (length(featureList != 0)) {
    bestResid = -1
    bestFeat = ""
    bestModel = NULL
    for (f in featureList) {
      model = lm(paste0(lmFormula, "+", f), data=mtcars)
      currResid = sum(residuals(model)^2)
      
      if (currResid < bestResid || bestResid == -1) {
        bestResid = currResid
        bestFeat = f
        bestModel = model
      }
    }
    
    if (lmFormula != paste0(tgt, "~")) {
      lmFormula = paste0(lmFormula, "+", bestFeat)
    } else {
      lmFormula = paste0(lmFormula, bestFeat)
    }
    
    modelList = c(modelList, list(bestModel))
    formulaList = c(formulaList, lmFormula)
    mseList = c(mseList, bestResid)
    
    featureList = featureList[featureList != bestFeat]
  }
  cbind(modelList[2:(length(modelList))], 
        formulaList[2:(length(modelList))],
        mseList[2:(length(modelList))])
}

```

## Introduction

This pitch deck describes the Shiny application: MTCars Linear Model Creation Kit. Its purpose is for visual EDA of fitting linear models on the MtCars dataset.

The tool has the following components.

*  **Control panel**: controls the number of features fit and the target feature, also toggles displays
*  **Density Plot of Fitted Residuals**: shows the density of fitted residuals over all fitted models
*  **Line Graph of Mean Squared Error**: shows MSE over all fitted models indexed by number of features fit, as well as the average and minimum MSEs.
*  **Table**: shows the linear model formula and its corresponding MSE.

In the backend, the program iteratively fits the linear model with the feature resulting in a minimum Mean Squared Error and stores the models, formulae, and MSE internally.

## Inputs

**Predictor Selector**: Allows user to select any of the features provided in mtcars, they are the following.
```{r}
colnames(mtcars)
```

**Feature Selector**: Allows user to select a range of features, between 1 and 10. If only one feature is selected, then only one feature will be displayed.

**Toggle Checkboxes**: Allows user to toggle the individual visuals on and off, quite self explanatory. 


## Density Plot 
- It displays the histograms of these models based on number of features used.
- The purpose of this plot is to see the concentration of residuals and how it changes as more features are fit. 

```{r, echo=FALSE}
selectModels <- modelList()[,1][1:10]
resId = NULL

for (i in c(1:length(selectModels))) {
  tempResid = data.frame(residuals(selectModels[[i]]))
  tempResid$deg = toString(i)
  colnames(tempResid) = c("residuals", "degree")
  if (is.null(resId)) {
    resId = tempResid
  } else {
    resId = rbind(resId, tempResid)
  }
}

ggplot(resId, aes(residuals, fill = degree)) + 
  geom_density(alpha=0.2, color=NA) +
  ggtitle("Density Plot of Fitted Residuals by Number of Features")

```

## MSE Line Graph
- It plots the MSE for each fit model, as well as its average and minimum.
- The purpose of this plot is to show how MSE reduces as more features are fit and ultimately to serve as a hockeystick analysis for selecting the number of features.

```{r, echo=FALSE}
selectMSE <- modelList()[,3][1:10]
mseDf <- data.frame(degree=1:10, MSE=unlist(selectMSE))

ggplot() + 
  geom_line(data = mseDf, aes(degree, MSE, color="MSE per Number of Features", linetype="Actual Values")) + 
  geom_point(data = mseDf, aes(degree, MSE, color="MSE per Number of Features")) + 
  geom_hline(aes(yintercept=mean(mseDf$MSE), color = "Mean MSE", linetype="Aggregates")) + 
  geom_hline(aes(yintercept=min(mseDf$MSE), color = "Min MSE", linetype="Aggregates")) + 
  scale_colour_manual(values = c("red", "purple", "blue")) +
  scale_linetype_manual(values = c("solid", "twodash")) +
  ggtitle("Means Squared Error by Number of Features Fitted")

```

